Supplementary Material for Asymmetry paper

### 2020-05-29 Supplementary/Sup_mat.Rmd
New power for Hoop Size
Power now samples from participants to simulate individual differences

The fit with the empirical data is reasonable, although we under-estimate the frequency of standing positions $\phi\approx0.5$, in this case 0.5 is considered the central point with 0 and 1 representing the left and right hoop respectively. We assumed that by introducing a difference in size between the two hoops that this distribution would shift towards the smaller hoop so as to balance their chances of success. We assumed that the difference in hoop size would cause particiapnts to stand slightly closer to the small hoop, in this case the shift in mean would be +0.05. 
```{r Hoop Size resampling, include = T, echo = F, cache = T}
# setup loop
n_iter <- 5000
n_subs <- seq(3, 24, 1)
n_trials <- 72

# for data.table
n <- n_iter * length(n_subs) * length(mu2) * length(n_trials)
df_sample <- data.table::data.table(iter = rep(0, n),
                                    n_subs = rep(0, n),
                                    n_trials = rep(0, n),
                                    difference = rep(0, n),
                                    baseline = rep(0, n),
                                    comparison = rep(0, n))

# loop for sampling
count <- 0
for(ii in 1:n_iter){
  base_shape <- get_shape_beta(mu1, var1)
  base_alpha <- base_shape$alpha
  base_beta <- base_shape$beta
  for(trials in n_trials){
    for(diff in mu2){
      comp_shape <- get_shape_beta(mu1 + diff, var1)
      comp_alpha <- comp_shape$alpha
      comp_beta <- comp_shape$beta
      for(sub in n_subs){
        # up count here
        count <- count + 1
        base_sample <- c()
        comp_sample <- c()
        for(s in 1:sub){
          base_sample <- c(base_sample, rbeta(n_trials, base_alpha, base_beta))
          comp_sample <- c(comp_sample, rbeta(n_trials, comp_alpha, comp_beta))
        }
        # df_sample <- rbind(df_sample, tibble(iter = ii,
        #                                      n_subs = sub,
        #                                      n_trials = trials,
        #                                      difference = diff,
        #                                      baseline = mean(base_sample),
        #                                      comparison = mean(comp_sample)))
        # add to table
        df_sample[count, iter := ii]
        df_sample[count, n_subs := sub]
        df_sample[count, n_trials := trials]
        df_sample[count, difference := diff]
        df_sample[count, baseline := mean(base_sample)]
        df_sample[count, comparison := mean(comp_sample)]
      }
    }
  }
}

@@

df_sample %>% 
  filter(difference == 0.05) %>% 
  group_by(n_subs) %>% 
  mutate(diff = comparison - baseline) %>% 
  summarise(mu = mean(diff), 
            lower = hdi(diff)[1],
            upper = hdi(diff)[2]) %>% 
  ggplot(aes(n_subs, mu)) + 
  geom_line() + 
  geom_ribbon(aes(ymin = lower,
                  ymax = upper),
              alpha = .3) + 
  scale_x_continuous("Sample Size") + 
  theme_bw() + 
  theme(axis.title.y = element_blank())

>>>>

The fit with the empirical data is reasonable, although we under-estimate the frequency of standing positions $\phi\approx0.5$, in this case 0.5 is considered the central point with 0 and 1 representing the left and right hoop respectively. We assumed that by introducing a difference in size between the two hoops that this distribution would shift towards the smaller hoop so as to balance their chances of success. We assumed that the difference in hoop size would cause particiapnts to stand slightly closer to the small hoop, in this case the shift in mean would be +0.05. 
```{r Hoop Size resampling, include = T, echo = F, cache = T}
# Need to sample each participant and get parameters for them 
temp <- df_part2 %>% 
  group_by(Participant) %>% 
  summarise(a = fitdistrplus::fitdist(beta_pos, "beta")$estimate[1],
            b = fitdistrplus::fitdist(beta_pos, "beta")$estimate[2])
mus <- seq(0, .2, .05)

df_distributions <- tibble(participant = rep(temp$Participant, each = length(mus)),
                           og_as = rep(temp$a, each = length(mus)),
                           og_bs = rep(temp$b, each = length(mus)),
                           og_mu = mu_beta(og_as, og_bs),
                           og_var = var_beta(og_as, og_bs),
                           increase = rep(mus, length(temp$a))) %>% 
  mutate(mu = og_mu + increase,
         var = og_var, 
         alpha = get_shape_beta(mu, var)$alpha,
         beta = get_shape_beta(mu, var)$beta) %>% 
  select(participant, increase, mu, var, alpha, beta)

# setup loop
diff_sample <- seq(.05, .2, .05)
n_iter <- 5000
n_subs <- seq(3, 25, 1)
n_trials <- 72
n <- length(diff_sample) * n_iter * length(n_subs)
refresh <- n_iter/100

df_sample <- data.table::data.table(iter = rep(0, n),
                                    increase = rep(0, n),
                                    n_subs = rep(0, n),
                                    n_trial = rep(0, n),
                                    base = rep(0, n),
                                    comp = rep(0, n))

# loop 
count <- 1

for(ii in 1:n_iter){
  for(inc in diff_sample){
    for(subN in n_subs){
      subs <- sample(unique(df_distributions$participant), subN, replace = T)
      baseline <- c()
      comparison <- c()
      for(sub_iter in 1:length(subs)){
        base_a <- df_distributions$alpha[df_distributions$participant == subs[sub_iter] &
                                           df_distributions$increase == 0]
        base_b <- df_distributions$beta[df_distributions$participant == subs[sub_iter] &
                                          df_distributions$increase == 0]
        comp_a <- df_distributions$alpha[df_distributions$participant == subs[sub_iter] &
                                           df_distributions$increase == inc]
        comp_b <- df_distributions$beta[df_distributions$participant == subs[sub_iter] &
                                          df_distributions$increase == inc]
        baseline <- c(baseline, rbeta(n_trials, base_a, base_b))
        comparison <- c(comparison, rbeta(n_trials, comp_a, comp_b))
      }
      df_sample[count, iter := ii]
      df_sample[count, increase := inc]
      df_sample[count, n_subs := subN]
      df_sample[count, n_trial := n_trials]
      df_sample[count, base := mean(baseline)]
      df_sample[count, comp := mean(comparison)]
      count <- count + 1
    }
  }
  # if(ii %% refresh == 0){
  #   print(paste((ii/n_iter)*100, "%", sep = ""))
  # }
}

@@

df_sample %>% 
  filter(increase == 0.05) %>% 
  group_by(n_subs) %>% 
  mutate(diff = comp - base) %>% 
  summarise(mu = mean(diff), 
            lower = hdi(diff)[1],
            upper = hdi(diff)[2]) %>% 
  ggplot(aes(n_subs, mu)) + 
  geom_line() + 
  geom_ribbon(aes(ymin = lower,
                  ymax = upper),
              alpha = .3) + 
  scale_x_continuous("Sample Size") + 
  theme_bw() + 
  theme(axis.title.y = element_blank())
